---
title: "My_doc"
author: "Hasna Alghamdi"
format: html
theme: yeti
execute:
  echo: true
  error: true
---

The table, regression results, and figure, with appropriate captions 
```{r}
#| message: false
#| warning: false

(install.packages("gtsummary", dependencies = TRUE))
library(gtsummary)
data <- read.csv(here::here("Data", "healthy_lifestyle_city_2021.csv"))

tbl_summary(
	data,
	include=
		c(City, Rank, Happiness_levels, Outdoor_activities,
						  YLE))
```

```{r}
#| label: tbl-one
#| tbl-cap: "This is a table of a dataframe"
knitr::kable(mtcars)
```


```{r}
#| label: hist
#| fig-cap: "This is a histogram"
hist(rnorm(100))
```
Cross-references to a table and a figure at least once each
```{r}
#| label: tbl-univarible-regression
#| tbl-cap: "Linear regression"
rank_tbl <- tbl_uvregression(
	data,
	y = Rank,
	include = c(Happiness_levels, Outdoor_activities,YLE
	),
	method = lm)
```
Table @tbl-univarible-regression shows the associations between happiness, outdoor activities, life expectancy, and city rank! 


Inline R code in at least 2 places, 1 pulling a statistic from a table (i.e., using gtsummary::inline_text()) and 1 printing something else (like we did with the mean age in the example)
```{r}
stats <-list(
	n= nrow(data),
	mean_YLE =mean(data$YLE, na.rm=TRUE),
	mean_happy=mean(data$Happiness_levels, na.rm=TRUE)
)
```
 There were `r stats$n` cities, with a mean of ife expectancy `r stats$mean_YLE`
 and a mean of happiness score of `r stats$mean_happy`
 
```{r}
inline_text(rank_tbl, variable= "YLE")
```
Life expectancy was not statistically significant with the city rank ("-0.78 (95% CI -1.5, -0.06; p=0.034)").

A brief description of the data, including its source 

**The data include 44 unique values, and 10 different columns**
It measures the association between the happiness level for each country, 
different variables like the Sunshine hours, Life expectancy(years),Outdoor activities
, and more.

**Healthy Lifestyle Cities Report 2021 from** https://www.lenstore.co.uk/research/healthy-lifestyle-report/
